---
title: "P1"
author: "AO Valdes"
output:
  html_document:
    highlight: kate
    theme: cosmo
    toc_depth: 5
  pdf_document:
    toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


$$
\int_\Omega f(\omega)d\omega=1
$$

For instance, this is a chunk;
```{r echo=FALSE}
s=3*2
s
```

This is another chunk
```{r}
s*2
```


```{r}
data("cars")
knitr::kable(head(cars))
```



##Markup

1. First ordered list item

2. Another item

⋅⋅* Unordered sub-list. 

1. Actual numbers don't matter, just that it's a number

⋅⋅1. Ordered sub-list

4. And another item.

5. Este fui yo

⋅⋅⋅You can have properly indented paragraphs within list items. Notice the blank line above, and the leading spaces (at least one, but we'll use three here to also align the raw Markdown).

⋅⋅⋅To have a line break without a paragraph, you will need to use two trailing spaces.⋅⋅
⋅⋅⋅Note that this line is separate, but within the same paragraph.⋅⋅
⋅⋅⋅(This is contrary to the typical GFM line break behaviour, where trailing spaces are not required.)

* Unordered list can use asterisks
- Or minuses
+ Or pluses

Paste a video with secundary click and clik in copiar codigo de insercion

<iframe width="878" height="494" src="https://www.youtube.com/embed/l1FJfr_spJQ" frameborder="0" allow="autoplay; encrypted-media" allowfullscreen></iframe>
